Global adjoint tomography -- Model GLAD-M25

### 2018-10-21 main.tex
Updates from ShareLaTeX

@@

\begin{figure}
\centering
\includegraphics[width=0.9\textwidth]{figures/depth_slice/america_vs.pdf}
  \caption{Map views of isotropic shear wavespeed variations beneath North America 
  for model GLAD-M25 (first column) and several global (S362ANI$+$M and S40RTS)
  and regional~\citep[US22;][]{zhu2017radial} and~\citep[SL2013NA;][]{schaeffer2014imaging}
  models. Green circles denote the locations of hotspots. For SL2013NA, we
  show a depth of 610~km instead of 600~km, reflecting its model parametrization.}
\label{fig:america-vs}

\end{figure}

@@

Fig.~\ref{fig:europe-vs} shows isotropic shear wavespeed perturbations beneath Europe.
For comparison,

In addition to our model GLAD-M25, S362ANI+M and S40RTS, we included a regional
tomography model EU60\citep{zhu2015seismic} into our comparison. The EU60 uses
adjoint methods to iteratively inverse the crust and upper mantle strcuture
beneath the European continent and North Atlantic Ocean, by assimilating
190 earthquakes and 745 seismic station.

Europe is featured by the Trans-European Suture Zone(TESZ), seperating the
Precambrian East Europen Craton(EEC) in the northeast and the Phanerozoic
europe in the southwest.  The TESZ is very consistent across all the models,
even though is much sharper in GLAD-M25 and EU60.

In the north, we observed the high velocity anomaly beneath Central Graben in the
North Sea, and clearly seperated from the EEC bounded at the western north, which is
explained as the lithospheric drip with delamination, as explained in
\cite{zhu2015seismic}.

@@

Moving furture to the east, at about 400km, there is clearlyfast anomaly lie beneath
the Dinarides Mountains,
sepating the Adria plate and Pannonian Basin and indicating the subudction of Adria
plate into the Euroasian plate. This anomaly get sharper at 600km. The southern
part of it interacts with the Hellenic Arc subductions, which penetrate the mantle
trasition zones and extend below 1,000 kms in our model. We will discuss the Hellenic
Arc in details in the later sections. The Pannonia Basin is featured by low velocity
anomaly at the depth from 100 to 250km, then gradually transferred to high velocity
due to the subduction of Adria plate. The Anatolia plate is shown as slow velocity
anomaly in our model, sharpened from two other global models.

@@

In the north of Atlantic Ocean, our model strengthed the slow anlomaly near the
Atlantic Ocean Ridge, especially at the Iceland and Azores. The Iceland, becomes
much strong in our model in the upper mantle from 250km to 400km, compared to
S362ANI+M, extending all the way to the mantle-transition zone. On the other hand,
Azores, is a much shallower hotspot, with the slow anomaly extend at about 250km.

>>>>

\begin{figure}
\centering
\includegraphics[width=0.9\textwidth]{figures/depth_slice/america_vs.pdf}
  \caption{Map views of isotropic shear wavespeed variations beneath North America 
  for model GLAD-M25 (first column) and several global (S362ANI$+$M and S40RTS)
  and regional~\citep[US22;][]{zhu2017radial} and~\citep[SL2013NA;][]{schaeffer2014imaging}
  models. Green circles denote the locations of hotspots. For SL2013NA, we
  show a depth of 610~km instead of 600~km, reflecting its model parametrization.}
\label{fig:america-vs}
\end{figure}

@@

@@

Fig.~\ref{fig:europe-vs} shows isotropic shear wavespeed perturbations beneath Europe.
In addition to our model GLAD-M25, S362ANI+M and S40RTS, we included a regional
tomography model EU60\citep{zhu2015seismic} into our comparison. The EU60 uses
adjoint methods to iteratively inverse the crust and upper mantle structure
beneath the European continent and North Atlantic Ocean, by assimilating
190 earthquakes and 745 seismic station.

Europe is featured by the Trans-European Suture Zone(TESZ), separating the
Precambrian East European Craton(EEC) in the northeast and the Phanerozoic
Europe in the southwest.  The TESZ is very consistent across all the models,
even though is much sharper in GLAD-M25 and EU60.

In the north, we observed the high velocity anomaly beneath Central Graben in the
North Sea, and clearly separated from the EEC bounded at the western north, which is
explained as the lithospheric drip with delamination, as explained in
\cite{zhu2015seismic}.

@@

Moving further to the east, at about 400km, there is clear fast anomaly lie
beneath the Dinarides Mountains, separating the Adria plate and Pannonian Basin, indicating the subduction of Adria plate into the Euroasian plate.
This anomaly get sharper at 600km. The southern
part of it interacts with the Hellenic Arc subductions, which penetrate the mantle
transition zones and extend below 1,000 km in our model. We will discuss the Hellenic
Arc in details in the later sections. The Pannonian Basin is featured by low velocity
anomaly at the depth from 100 to 250km, then gradually transferred to high velocity
due to the subduction of Adria plate. The Anatolia plate is shown as slow velocity
anomaly in our model, sharpened from two other global models.

@@

In the north of Atlantic Ocean, our model strengthened the slow anomaly near the
Atlantic Ocean Ridge, especially at the Iceland and Azores. The Iceland, becomes
much strong in our model in the upper mantle from 250km to 400km, compared to
S362ANI+M, extending all the way to the mantle-transition zone. On the other hand,
Azores, is a much shallower hotspot, with the slow anomaly extend at about 250km.
